MS_CNuptake.Rmd

### 2023-05-19 MS_CNuptake.Rmd
adjusted r2 updated in stepwise_lm function

@@

#final nue - calculated from final results
#forest nue:
(55.74/0.61) 
#grassland nue:
(16.36/0.34)
#total nue:
76.01 # as calculated above
#forest nue uncertainty:
(55.74/0.61)  * sqrt( (10.62/55.74)^2 +(0.22/0.61)^2)
#grassland nue uncertainty:
(16.36/0.34) * sqrt( (9.72/16.36)^2 +(0.15/0.34)^2)
#pft
(72.10/0.95) * sqrt( (14.40/72.10)^2 +(0.26/0.95)^2)
```

>>>>

total_value

@@

#final nue - calculated from final results
#forest nue:
(55.74/0.61) 
#grassland nue:
(16.36/0.34)
#total nue:
76.00 # as shown in figure
#forest nue uncertainty:
(55.74/0.61)  * sqrt( (10.62/55.74)^2 +(0.22/0.61)^2)
#grassland nue uncertainty:
(16.36/0.34) * sqrt( (9.72/16.36)^2 +(0.15/0.34)^2)
#pft
(72.10/0.95) * sqrt( (14.40/72.10)^2 +(0.26/0.95)^2)
```
